---
title: "shiny project"
author: "MianchunLu"
date: "October 8, 2019"
output: html_document
---

```{r}
#install.packages("shiny")
#install.packages("RColorBrewer")
library(RColorBrewer)
library(shiny)
library(lubridate)
library(leaflet)
library(treemap)
library(data.table)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(ggmap)
library(stringr)
library(png)
```

```{r}
## Set the API so that I can use geocode()
```

### load movie events data
```{r}
setwd()
data14 <- fread('Chicago_Park_District__Movies_in_the_Parks_2014.csv')
data15 <- fread('Chicago_Park_District__Movies_in_the_Parks_2015.csv')
data16 <- fread('Chicago_Park_District__Movies_in_the_Parks_2016.csv')
data17 <- fread('Chicago_Park_District__Movies_in_the_Parks_2017.csv')
data18 <- fread('Chicago_Park_District__Movies_in_the_Parks_2018.csv')
data19 <- fread('Chicago_Park_District__Movies_in_the_Parks_2019.csv')
```

### merge the data in different year together and correct the data format
```{r}
col=c('StartDate',"ParkName", "Phone", "MovieName", "MovieClosedCaption", "MovieRating", "ParkAddress", "CommunityAreas", "ZipCode", "Wards", "Year")

# Since the event data each year was downloaded from open data source respectively, extra data cleaning steps are needed to alter them into unified format.

# 2014
colnames(data14)[colnames(data14)=="Location"]="ParkName"
colnames(data14)[colnames(data14)=="Location 1"]="ParkAddress"
colnames(data14)[colnames(data14)=="Community Areas"]="CommunityAreas"
colnames(data14)[colnames(data14)=="Zip Codes"]="ZipCode"
data14$"Year"="2014"
data14$StartDate=substr(data14$StartDate,1,10)
data14$StartDate=mdy(data14$StartDate)

# 2015
colnames(data15)[colnames(data15)=="Location 1"]="ParkAddress"
colnames(data15)[colnames(data15)=="Community Areas"]="CommunityAreas"
colnames(data15)[colnames(data15)=="Zip Codes"]="ZipCode"
data15$"Year"="2015"
data15$StartDate=substr(data15$StartDate,1,10)
data15$StartDate=mdy(data15$StartDate)

# 2016
colnames(data16)[colnames(data16)=="Location"]="ParkName"
colnames(data16)[colnames(data16)=="Location 1"]="ParkAddress"
colnames(data16)[colnames(data16)=="Community Areas"]="CommunityAreas"
colnames(data16)[colnames(data16)=="Zip Codes"]="ZipCode"
data16$"Year"="2016"
data16$StartDate=mdy(data16$StartDate)

# 2017
colnames(data17)[colnames(data17)=="Date"]="StartDate"
colnames(data17)[colnames(data17)=="Park"]="ParkName"
colnames(data17)[colnames(data17)=="Park Phone"]="Phone"
colnames(data17)[colnames(data17)=="Title"]="MovieName"
colnames(data17)[colnames(data17)=="CC"]="MovieClosedCaption"
colnames(data17)[colnames(data17)=="Rating"]="MovieRating"
colnames(data17)[colnames(data17)=="Park Address"]="ParkAddress"
colnames(data17)[colnames(data17)=="Community Areas"]="CommunityAreas"
colnames(data17)[colnames(data17)=="Zip Codes"]="ZipCode"
data17$"Year"="2017"
data17$StartDate=mdy(data17$StartDate)

# 2018
colnames(data18)[colnames(data18)=="Date"]="StartDate"
colnames(data18)[colnames(data18)=="Park"]="ParkName"
colnames(data18)[colnames(data18)=="Park Phone"]="Phone"
colnames(data18)[colnames(data18)=="Title"]="MovieName"
colnames(data18)[colnames(data18)=="CC"]="MovieClosedCaption"
colnames(data18)[colnames(data18)=="Rating"]="MovieRating"
colnames(data18)[colnames(data18)=="Park Address"]="ParkAddress"
colnames(data18)[colnames(data18)=="Community Areas"]="CommunityAreas"
colnames(data18)[colnames(data18)=="Zip Codes"]="ZipCode"
data18$"Year"="2018"
data18$StartDate=mdy(data18$StartDate)

# 2019
colnames(data19)[colnames(data19)=="Date"]="StartDate"
colnames(data19)[colnames(data19)=="Park"]="ParkName"
colnames(data19)[colnames(data19)=="Park Phone"]="Phone"
colnames(data19)[colnames(data19)=="Title"]="MovieName"
colnames(data19)[colnames(data19)=="CC"]="MovieClosedCaption"
colnames(data19)[colnames(data19)=="Rating"]="MovieRating"
colnames(data19)[colnames(data19)=="Park Address"]="ParkAddress"
colnames(data19)[colnames(data19)=="Community Areas"]="CommunityAreas"
colnames(data19)[colnames(data19)=="Zip Codes"]="ZipCode"
data19$"Year"="2019"
data19$StartDate=mdy(data19$StartDate)

l=list(data14[, col,with=FALSE], data15[, col,with=FALSE], data16[, col,with=FALSE], data17[, col,with=FALSE], data18[, col,with=FALSE], data19[, col,with=FALSE])
data = rbindlist(l)

## get the monthe and weekday
data$Weekday=wday(data$StartDate, label=TRUE, abbr=FALSE)
data$month=month(data$StartDate,label=T)

## convert the location into latitude and longitude
data$longitude=geocode(data$ParkName)$lon
data$latitude=geocode(data$ParkName)$lat

## make sure the data in the same format
data[MovieClosedCaption=="Y"]$MovieClosedCaption="Yes"
data[MovieClosedCaption=="N"]$MovieClosedCaption="No"

data$CommunityAreas=as.character(data$CommunityAreas)

fwrite(data, "MovieInPark14-19.csv")
data=fread("MovieInPark14-19.csv")
```

### First page: map of "movie in park" event in Chicago each year
button: check box--year, checkbox--weekday
interactive map: show information of the park, and the number of events and details about each event(movie name)
```{r}
## test the interactive map
leaflet()%>%
  setView(lng = -87.6, lat = 41.9, zoom = 13)%>% 
  addTiles()%>%addProviderTiles(providers$Hydda.Full)

a<-data[, .(count = .N, val = list(MovieName)), by = c("ParkName","longitude","latitude")]

a$information=paste("<h2>","<b>",a$ParkName,"</b>","</h2>",
                    "The number of events:", "<b>",a$count,"</b>","<br/>","<br/>",
                    "<b>Movies include:</b>","</br>",
                    a$val)
a$information=str_remove(a$information,"c\\(")

a1=a[a$count==1]
a2=a[a$count>1]
a2$information=substr(a2$information, 1, nchar(a2$information)-1)
a3=rbind(a1,a2)

## single color
leaflet(a3)%>%
        setView(lng = -87.6, lat = 41.9, zoom = 11)%>% 
        addTiles()%>%
        addProviderTiles(providers$Hydda.Full)%>%
        addMarkers(~longitude, ~latitude, popup = ~information) 

## multiple colors
getColor <- function(a3) {
  sapply(a3$count, function(count) {
  if(count <= 4) {
    "green"
  } else if(count <= 6) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(a3)
)

leaflet(a3)%>%
        setView(lng = -87.6, lat = 41.9, zoom = 11)%>% 
        addTiles()%>%
        addProviderTiles(providers$Hydda.Full)%>%
        addAwesomeMarkers(~longitude, ~latitude, icon=icons,popup = ~information) 
```

### Second page: statistics graphs
```{r}
## weekday--count
data %>%
  select(Weekday)%>%
  group_by(Weekday)%>%
  ggplot(aes(x=Weekday))+
  geom_bar(fill="#FF9999")+
  scale_x_discrete(limits=c("Monday","Tuesday","Wednesday","Thursday", "Friday","Saturday","Sunday"))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

## Year--count
data %>%
  select(Year)%>%
  group_by(Year)%>%
  ggplot(aes(x=Year))+
  geom_bar(fill="#FF9999")+
  scale_x_discrete(limits=c("2014","2015","2016","2017", "2018","2019"))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

## Month--count
data %>%
  select(month)%>%
  group_by(month)%>%
  ggplot(aes(x=month))+
  geom_bar(fill="#FF9999")+
  scale_x_discrete(limits=c("Jan","Feb","Mar","Apr", "May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

## community areas & year & count ---- tree map
data$CommunityAreas=as.character(data$CommunityAreas)
tmp=data[, .(count=.N),by="CommunityAreas"]
tmp=tmp[CommunityAreas!=""]
tmp$info=paste("Area No.",tmp$CommunityAreas,", ","Events: ",tmp$count,sep="")
fwrite(tmp, "maptree_data.csv")
tmp=fread("maptree_data.csv")
tmp$CommunityAreas=as.character(tmp$CommunityAreas)
treemap(tmp,index="info",vSize="count",vColor="CommunityAreas",type="categorical",palette="RdYlBu",
        drop.unused.levels = FALSE, position.legend="none",fontsize.labels=8)

## MovieRating & MovieClosedCaption
p1<-data %>%
  select(MovieRating)%>%
  filter(MovieRating!="N/A" & MovieRating != "")%>%
  group_by(MovieRating)%>%
  ggplot(aes(x=MovieRating))+
  geom_bar(fill="#FF9999")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

p2<-data %>%
  select(MovieClosedCaption)%>%
  filter(MovieClosedCaption!="N/A" & MovieClosedCaption != "")%>%
  group_by(MovieClosedCaption)%>%
  ggplot(aes(x=MovieClosedCaption))+
  geom_bar(fill="#FF9999")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

grid.arrange(p1, p2, nrow = 1)


## MovieName--top 
tmp=data[, .(count=.N),by=MovieName]
nb.cols <- 40
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)

tmp%>%
  arrange(desc(count)) %>%
  slice(1:20)%>%
  ggplot(aes(x=reorder(MovieName,count), y=count,fill=factor(MovieName)))+
              geom_bar(stat='identity')+coord_flip()+theme_light()+theme(legend.position="none")+
  scale_fill_manual(values = mycolors)
```


### Add a real map of City of Chicago to the treemap
```{r}
img(src = "community_areas.png",width="100%")
```

